### 2024-01-03 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 1 Jan 2024
Updated thesis 4 Jan 2024

Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the HL-LHC. The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle. The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors. The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation. The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz. The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made. The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.

The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules (modules with two readout chips) and 504 units of \( 2 \times 2 \) modules (modules with four readout chips) arranged in four layers parallel to the beam. The TFPX extends from approximately 250~mm to 1400~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules. The TEPX covers a range from about 1700~mm to over 2600~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules. Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.

The TEPX consists of four double-disk per side with each double-disk consisting of five rings of modules as shown in Fig. \ref{fig:Innertracker_40}. %The rings have 20, 28, 36, 44 and 48 modules respectively.
The first two inner rings are equipped with \(1 \times 2\) modules, while the more extensive \(2 \times 2\) modules are mounted on the three outer rings. This design is further enhanced by the arrangement of modules in four layers as shown in Fig. \ref{fig:Innertracker_41}. This allows for modules to be mounted on both the front and back sides of a disk, creating an overlap in the r-\(\phi\) direction. By mounting modules at varying radii on the two disk that form each double-disk, overlap in the radial direction (r) is also accomplished. TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.

@@

\begin{figure}[!htp]
  \centering
  \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
  \label{fig:Innertracker}
\end{figure}

@@

\newpage
\section{TEPX Luminometer}

@@

Fig. \ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200 \cite{dabrowski2020}. %Clusters refer to groups of hits in the pixel detector.
It consists of five concentric rings that are color-coded to indicate the density of clusters within the detector. It is transitioning from blue (low density) to red (high density), with the hottest regions indicating the overlap modules within the rings. The granularity of the histogram is set to 1000 for both axes and a bin size of 0.1 cm, allowing for a detailed visualization of the clusters across the disk.
%The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_1.png}
  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
    It shows clusters in one TEPX disk consisting of 5 rings. Hot regions are showing the module overlap. %for all rings (red, orange, green, yellow). Number of x bins is 1000, x bins range from -40 to 40.
    x bin size is 0.1 cm and %Number of y bins is 1000, y bins range from -40 to 40.
    y bin size is 0.1 cm.}
  \label{fig:tepx_cl}
\end{figure}

@@

We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, phi variable for pileup 0.5. Based on pileup 0.5 sample, a pre-selection of 0.15 cm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_1.png}
\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & dphi]{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for Disk 4 Ring 1. The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
}
\label{fig:cluster_dr_dphi_dist}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption[dr offset values]{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr cut values for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

@@

\newpage
\begin{table}[H]
  \centering
  \caption[dr mean values]{dr mean values (cm) obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\ 
%-3 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\ 
%-2 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\ 
%-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
1 & 0.023 & 0.031 & 0.039 & 0.047 \\
2 & 0.020 & 0.027 & 0.034 & 0.040 \\
3 & 0.018 & 0.023 & 0.029 & 0.035 \\
4 & 0.015 & 0.020  & 0.026 & 0.031 \\
\end{tabular}
\label{tab:my_label_55}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr standard deviation (cm) values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
1 & 0.0045 & 0.0045 & 0.0047 & 0.0052 \\
2 & 0.00442 & 0.0047 & 0.0048 & 0.0050 \\
3 & 0.0045 & 0.0045 & 0.0049 & 0.0049 \\
4 & 0.0045 & 0.0047 & 0.0049 & 0.0049 \\
\end{tabular}
\label{tab:my_label_53}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                            
  Map of two fold coincidences in phi showing all module overlap regions.
}
\label{fig:cluster_ring_720}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
\caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%                                                                                                                                                                                      
   X-Y map of reconstructed two-fold coincidences in r using the selections described in the text. We have only reconstructed coincidences in r arising from module overlap in L1L2 and L3L4. The gaps in the plot correspond to other types of two fold coincidences in r that will arise from module overlap in L1L4, L3L4 and L2L3.
}
\label{fig:cluster_ring_79}
\end{figure}

@@

It is possible to have three fold coincidences in TEPX detector. A three-fold coincidence refers to a situation where three hits occur in a close spatial arrangement originating from the same underlying event. In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi or r is found. The XY map of three-fold coincidences is shown in Fig. \ref{fig:tepx_3foldcoin_allPU_1}. Three-fold coincidences under all pileup conditions is shown in Fig.  \ref{fig:tepx_3foldcoin_allPU_2}.  With the current algorithm, three-fold coincidences shows non-linearity as shown in Fig. \ref{fig:tepx_3foldcoin_allPU_3}. % and Fig.  \ref{fig:tepx_3foldcoin_lowPU}.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{ashish_thesis/tepx_threefold_coincidences.png}
  \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}
  \label{fig:tepx_3foldcoin_allPU_1}
\end{figure}

>>>>

Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the HL-LHC. The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle. The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors. The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation. The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz. The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made. %The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
In the Inner Tracker readout system, control signals are sent to the it at 160 Mb/s to coordinate its detection processes. It, in turn, outputs data at 1.28 Gb/s per chip to the LpGBT, which acts as a data consolidator for up to three chips. This data is then relayed optically to the DTC board, which operates a bidirectional data exchange: 2.5 Gb/s optical down-links channel control information back to the Inner Tracker, while 10 Gb/s up-links carry processed readout data and monitoring details to the DAQ and control system. Moreover, the DTC can interface with a Lumi processor via an optional link, designed for a substantial data transfer rate of approximately 4x25 Gb/s, to handle specialized luminosity data processing. Finally, the DAQ and control system, which receives the comprehensive data at a substantial rate of 25 Gb/s, undertakes the final processing and storage of data.

The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing \( 1 \times 2 \) modules (modules with two readout chips) and \( 2 \times 2 \) modules (modules with four readout chips) arranged in four layers parallel to the beam. The TFPX extends from approximately 250~mm to 1400~mm in the \( z \)-direction, with \( 1 \times 2 \) and \( 2 \times 2 \) modules. The TEPX covers a range from about 1700~mm to over 2600~mm and includes  \( 1 \times 2 \) and \( 2 \times 2 \) modules. Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.

The TEPX consists of four double-disk per side with each double-disk consisting of five rings of modules as shown in Fig. \ref{fig:Innertracker_40}. The rings have 20, 28, 36, 44 and 48 modules respectively.
The first two inner rings are equipped with \(1 \times 2\) modules, while the more extensive \(2 \times 2\) modules are mounted on the three outer rings. This design is further enhanced by the arrangement of modules in four layers as shown in Fig. \ref{fig:Innertracker_41}. This allows for modules to be mounted on both the front and back sides of a disk, creating an overlap in the r-\(\phi\) direction. By mounting modules at varying radii on the two disk that form each double-disk, overlap in the radial direction (r) is also accomplished. TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
  \label{fig:Innertracker}
\end{figure}

@@

\section{TEPX Luminometer}

@@

Fig. \ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200 \cite{dabrowski2020}. %Clusters refer to groups of hits in the pixel detector.
It consists of five concentric rings that are color-coded to indicate the density of clusters within the detector. It is transitioning from blue (low density) to red (high density), with the hottest regions indicating the overlap modules within the rings. The granularity of the histogram is set to 1000 for both axes and a bin size of 0.1 mm, allowing for a detailed visualization of the clusters across the disk.
%The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_2.png}
  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
    It shows clusters in one TEPX disk consisting of 5 rings. Hot regions are showing the module overlap. %for all rings (red, orange, green, yellow). Number of x bins is 1000, x bins range from -40 to 40.
    x bin size is 0.1 mm and %Number of y bins is 1000, y bins range from -40 to 40.
    y bin size is 0.1 mm.}
  \label{fig:tepx_cl}
\end{figure}

@@

We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, phi variable for pileup 0.5. Based on pileup 0.5 sample, a pre-selection of 0.15 mm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & dphi]{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for Disk 4 Ring 1. The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
}
\label{fig:cluster_dr_dphi_dist}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption[dr offset values]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
  \end{tabular}
  \label{tab:mdr_cuts_offset_values}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
  \end{tabular}
  \label{tab:disk_values}
\end{table}

@@

\newpage
\begin{table}[H]
  \centering
  \caption[dr mean values]{dr mean values (mm) obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\ 
%-3 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\ 
%-2 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\ 
%-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
1 & 0.023 & 0.031 & 0.039 & 0.047 \\
2 & 0.020 & 0.027 & 0.034 & 0.040 \\
3 & 0.018 & 0.023 & 0.029 & 0.035 \\
4 & 0.015 & 0.020  & 0.026 & 0.031 \\
\end{tabular}
\label{tab:my_label_55}
\end{table}

\begin{table}[H]
  \centering
  \caption[dr cut values]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
\begin{tabular}{ccccc}
 & \multicolumn{4}{c}{\textbf{Ring}} \\
\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
\hline
%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
1 & 0.0045 & 0.0045 & 0.0047 & 0.0052 \\
2 & 0.00442 & 0.0047 & 0.0048 & 0.0050 \\
3 & 0.0045 & 0.0045 & 0.0049 & 0.0049 \\
4 & 0.0045 & 0.0047 & 0.0049 & 0.0049 \\
\end{tabular}
\label{tab:my_label_53}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                            
   X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
}
\label{fig:cluster_ring_720}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr_2.png}
\caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%                                                                                                                                                                                      
   X-Y map of reconstructed two-fold coincidences in r using the selections described in the text. We have only reconstructed coincidences in r arising from module overlap in L1L2 and L3L4. The gaps in the plot correspond to other types of two fold coincidences in r that will arise from module overlap in L1L4, L3L4 and L2L3.
}
\label{fig:cluster_ring_79}
\end{figure}

@@

It is possible to have three fold coincidences in TEPX detector. A three-fold coincidence refers to a situation where three hits occur in a close spatial arrangement originating from the same underlying event. In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi is found. The selections used for finding three-fold coincidences using old dx, dy and dz cut variables are 0.1 mm, 0.1 mm and 0.9 mm. The XY map of three-fold coincidences is shown in Fig. \ref{fig:tepx_3foldcoin_allPU_1}. Three-fold coincidences under all pileup conditions is shown in Fig.  \ref{fig:tepx_3foldcoin_allPU_2}.  With the current algorithm, three-fold coincidences shows non-linearity as shown in Fig. \ref{fig:tepx_3foldcoin_allPU_3}. % and Fig.  \ref{fig:tepx_3foldcoin_lowPU}.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\columnwidth]{ashish_thesis/tepx_threefold_coincidences_1.png}
  \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}
  \label{fig:tepx_3foldcoin_allPU_1}
\end{figure}
